Bureaucratic discrimination stemming from Islamophobia needs to be highlighted

### 2024-02-14 outputs/paper/paper.qmd
Update paper(Data section)

The original study, “The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Acces (2020) by Olsen, Kyhse-Anderson, Moynihan”, experimented with the unequal opportunities brought about by bureaucratic discrimination in Danish primary schools. Before the experiment, Olsen, Kyhse-Anderson, Moynihan defined bureaucratic discrimination as two forms: either through withholding opportunities in service or imposing administrative burdens to make bureaucratic procedures more complex and difficult. As a result, the original study revealed that individuals with Muslim names experience both forms of bureaucratic discrimination more frequently than those with native (Danish) names.

Our paper will reproduce these findings and will focus on the potential administrative discrimination against Muslims in Canada by building on the two forms of administrative discrimination (1. withholding opportunities in service, 2. imposing administrative burdens to make bureaucratic procedures more complex and difficult) Through the original experiment’s results, we discovered that administrative discrimination against Muslims could be driven by Islamophobic attitudes. Based on the two forms of bureaucratic discrimination defined in the original experiment, our study aims to assess perceptions of Muslims in Canada and discuss the potential for widespread administrative discrimination against Muslims.

@@

This paper reproduces two results from "The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Access(2020) by Olsen, Kyhse-Anderson, Moyni-han" in the American Journal of Social Science.
In the original study, the results showed disparities in decision type rates, compliance cost rates, and psychological cost rates. 
For the decision type, response emails were classified into three categories: clear reject, unclear response, and clear accept.(Examples 1-4 in Appendix A illustrate unclear responses)
As for compliance cost, it was categorized into four groups based on the format of the email content: simple question, complex question, request a phone call, and request to meet. Since decision type rates and compliance cost rates represent two forms of administrative discrimination above, our study will also verify these two sets of results and discuss the potential administrative discrimination against Muslims in Canada.

>>>>

The original study, “The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Acces (2020) by Olsen, Kyhse-Anderson, Moynihan”, experimented with the unequal opportunities brought about by bureaucratic discrimination in Danish primary schools.Before the experiment, Olsen, Kyhse-Anderson, Moynihan defined bureaucratic discrimination as two forms: either through withholding opportunities in service or imposing administrative burdens to make bureaucratic procedures more complex and difficult. As a result, the original study revealed that individuals with Muslim names experience both forms of bureaucratic discrimination more frequently than those with native (Danish) names.

Our paper will reproduce these findings and will focus on the potential administrative discrimination against Muslims in Canada by building on the two forms of administrative discrimination (1. withholding opportunities in service, 2. imposing administrative burdens to make bureaucratic procedures more complex and difficult). Through the original experiment’s results, we discovered that administrative discrimination against Muslims could be driven by Islamophobic attitudes. Based on the two forms of bureaucratic discrimination defined in the original experiment, our study aims to assess perceptions of Muslims in Canada and discuss the potential for widespread administrative discrimination against Muslims.

@@

This paper reproduces two results from "The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Access(2020) by Olsen, Kyhse-Anderson, Moyni-han" in the American Journal of Social Science.
In the original study, the results showed disparities in decision type rates, compliance cost rates, and psychological cost rates between Muslim and Danish. 
For the decision type, response emails were classified into three categories: clear reject, unclear response, and clear accept.(Examples 1-4 in Appendix A illustrate unclear responses)
Also, for compliance cost, it was categorized into four groups based on the format of the email content: simple question, complex question, request a phone call, and request to meet. Since the difference of decision type rates and compliance cost rates between Danish and Muslim represent two forms of administrative discrimination mentioned above, our study will also verify these two sets of results and discuss the potential administrative discrimination against Muslims in Canada.
